\sys: Light-touch Data-Parallel Shell Processing

### 2020-09-27 pldi/draft.tex
Remove manual split from section 5

\heading{Splitting Challenges}
\sys's optimizer inserts \ttt{split} nodes to expose parallelism when parallelizable nodes only have one input~\sx{ir:transformations}.
For \ttt{split} to be effective, it needs to disperse its input uniformly across its outputs.
This requires the input size to be known beforehand, which is not always the case.

To solve this, % satisfy the tension between efficiency and \todo{knowledge},  % blanking on the right word here
  \sys supports two \ttt{split} implementations:
  (i) a general one that can be used with commands that could add or remove lines, and
  (ii) an optimized one that can be used if the input size is known before its execution.
%% The \sys \todo{backend} support two split node implementations, to
%% satisfy the inherent tension between the split efficiency and
%% task-based parallelism.
In the former case, \ttt{split} first consumes its complete input, counts its lines, and then splits it uniformly across the desired number of outputs.
In the latter case, it can be configured to avoid reading all its input, thus exploiting available task-based parallelism.

\sys also inserts eager \ttt{relay} nodes after all \ttt{split} outputs (except the last one) to address laziness concerns.

>>>>

\heading{Splitting Challenges}
\sys's optimizer inserts \ttt{split} nodes to expose parallelism when parallelizable nodes only have one input~\sx{ir:transformations}.
For \ttt{split} to be effective, it needs to disperse its input uniformly across its outputs.
This requires the input size to be known beforehand, which is not always the case.
To address this, \sys provides a \ttt{split} implementations that first
consumes its complete input, counts its lines, 
and then splits it uniformly across the desired number of outputs. 
% This \ttt{split} can
% be used with any commands that add or remove lines in their output streams.
  % (i) a general one that can be used with commands that could add or remove lines, and
  % (ii) an optimized one that can be used if the input size is known before its execution.
%% The \sys \todo{backend} support two split node implementations, to
%% satisfy the inherent tension between the split efficiency and
%% task-based parallelism.
% In the latter case, it can be configured to avoid reading all its input, thus exploiting available task-based parallelism.
\sys also inserts eager \ttt{relay} nodes after all \ttt{split} outputs (except the last one) to address laziness concerns.
